\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-14 paper.tex
Refactor Trading Model introduction section

\section{\normalsize\textbf{Trading Model}}
In the following, we describe the data trading process in detail and we would use game theory to ensure the sustainability of our tading model. To participate a data marketplace, data providers and consumers have to register first. Then data provider can launch its product on the marketplace. Once a product is launched, it is searchable and can be subsequently traded. The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.

The consumer will pay for the data, only when the data sold by the data provider sufficiently accurate, for which we called such data "decent data."
Once the accuracy is lower than a certain threshold, which we call "unacceptable data," the consumers would then consider this data provider as a low quality data provider, and stop buying data from this data provider.

Refunds are a major issue in our research. However, we don't have to take refund as a factor in our game theory model, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data. The subscription fee will be paid as new data is transmitted to consumers. In other words, data provider doesn't need to take any procedure to transfer subscription fee from his/her own account to consumers' account. For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID documents and public keys. Everyone can query participants' public keys. Those who would like to sell or purchase data may register to become a data provider or consumer. The registrar has the authority to agree with applications. After that, their identities are available in the Registration Contract and the launching and trading processes can begin.

\subsection{Launching and Searching Products}
To sell streaming data, a data provider needs to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}. 
MAM allows users to create multiple channels as possible, however, the size of a channel is fixed which is decided before creation. Therefore, data providers should decide how to distribute data product into MAM channels, then determine a trusted broker to create a new MAM channel and Product Contract for recording the participants, subscription price brokerage fee, quantity of data and trading process.

>>>>

\section{\normalsize\textbf{Trading Model}}
In the following, we describe the data trading process in detail and adapt game theory to ensure the sustainability of our tading model. To participate a data marketplace, data providers and consumers have to register first. Then data provider can launch its product on the marketplace. Once a product is launched, it is searchable and can be subsequently traded. The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.

To evaluate trading model with game theory, we divide every piece of data products into two categories by the quality and accuracy, the \textbf{decent data} that consumers are willing to buy and \textbf{unacceptable data} that consumers would stop buying. Though refund is a major topic in our research, it is not discussed in game theory evaluation section. Since consumers pay off once to Purchase Contract for each merchandise, the subscription fee is either paid to providers or returned automatically. That is, both providers and consumers do not charge for extra fees during refund process.

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID documents and public keys. Everyone can query others' public keys for validation but only registrars have permission to add new members. After registration, the launching and trading processes can begin.

\subsection{Launching and Searching Products}
To sell streaming data, a data provider needs to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}. 
MAM allows users to create multiple channels as possible, however, the size of a channel is fixed which is decided before creation. Therefore, data providers should decide how to distribute data product into MAM channels, then determine a trusted broker to create a new one and a  Product Contract that records the participants, subscription price, brokerage fee, MAM channel session key, quantity of data and trading process.
